Camila Title Suggestions?

### 2019-05-14 manuscript/journal-applied-entomology/main.tex
Added in figures and captions to manuscript.

% Update article type if known
\papertype{Original Article}
% Include section in journal if known, otherwise delete
\paperfield{Journal Section}

@@

\begin{figure}[bt]
\centering
\includegraphics[width=6cm]{example-image-rectangle}
\caption{Although we encourage authors to send us the highest-quality figures possible, for peer-review purposes we are can accept a wide variety of formats, sizes, and resolutions. Legends should be concise but comprehensive – the figure and its legend must be understandable without reference to the text. Include definitions of any symbols used and define/explain all abbreviations and units of measurement.}
\end{figure}

>>>>

% Update article type if known
\papertype{Original Article}
% Include section in journal if known, otherwise delete
%\paperfield{Journal Section}

@@

\begin{figure}[bt]
\centering
\includegraphics[width = 8cm]{figures/publication/figure-1.pdf}
\caption{Adult onion maggot fly catch on sticky traps of different shape.  Shaded points denote raw values while solid points and error bars denote mean and bootstrapped 95\% confidence intervals respectively.  Letters not shared between groups denote significant differences in female trap catch (there was no observed difference in male trap catch) at $\alpha$ = 0.05 with Tukey's HSD test. }
\label{fig:figure1}
\end{figure}

\begin{figure}[bt]
\centering
\includegraphics[width = 8cm]{figures/publication/figure-2.pdf}
\caption{Adult onion maggot fly catch on spherical sticky traps of different size.  Points and error bars denote mean and 95\% confidence intervals respectively.  Letters not shared between groups indicates significant differences in adult catch at $\alpha$ = 0.05 with Tukey's HSD test.}
\label{fig:figure2}
\end{figure}

\begin{figure}[bt]
\centering
\includegraphics[width = 8cm]{figures/publication/figure-3.pdf}
\caption{Adult onion maggot fly catch on spherical sticky traps of different color.  Shaded points denote raw values while solid points and error bars denote means and bootstrapped 95\% confidence intervals respectively.  \textbf{*} indicates significantly different trap catch on white sticky traps (P = 0.012).}
\label{fig:figure3}
\end{figure}

\begin{figure}[bt]
\centering
\includegraphics[width = 8cm]{figures/publication/figure-4.pdf}
\caption{Adult onion maggot fly catch on sticky traps baited with Delia Lure attractant and unbaited.  Shaded points denote raw values while solid points and error bars denote means and bootstrapped 95\% confidence intervals respectively.  \textbf{*} indicates significantly different trap catch on baited and unbaited traps (P = 0.030). }
\label{fig:figure4}
\end{figure}
